Dependent Object Types

### 2012-08-05 article.tex
discuss methods vs lambda

>>>>

\subsubsection{Why not include the lambda-calculus instead of methods?}

Originally, the DOT calculus included the lambda-calculus, and
explicit methods were not needed since they could be represented by a
value label with a function type. However, the expansion of the
function type was defined to be the empty set of declarations (like
for $\Top$), which caused a real breach of type-safety.

A concrete object could be a subtype of a function type without a
function ever being defined. Consider:
\begin{align*}
&\mlnew u {\Top \refine z {\Ldecl C {\Top \tfun \Top} {\Top \tfun \Top}} \ldefs{}} {
\mlnew f {u.C \ldefs{}} {
\ldots
}}
\end{align*}

Now, $f$ is a subtype of $\Top \tfun \Top$, but $\app f {(\abs x \Top
  x)}$ is stuck (and, rightfully, doesn't typecheck). But we can use
narrowing to create a counterexample to type safety: $\app {(\abs g
  {\Top \tfun \Top} {\app g (\abs x \Top x)})} f$.

Because of this complication, we decided to drop the lambda-calculus
from DOT, and instead introduce methods with one parameter. Like in
Scala, functions are then just sugar for objects with a special
method.

An alternative design would have been to change the expansion of the
function type to have a special marker value label.
